General constraints on magic distillation protocols from statistical mechanics

### 2021-06-05 magic_paper.tex
introduced schur-convexity of D_alpha which facilitates the remaining proofs

@@

1. We need to prove that
\begin{equation}
	\sum_{\bmx} W_{\tau}(\bmx) W_{\rho|\tau}(\x)^\alpha \geq 1.
\end{equation}
\nick{How do we do this, while respecting the constraints on $\alpha$?}

2. Assume $D_\alpha (\rho,\tau) = 0$.
Then,
\begin{equation}
	\sum_{\bmx} W_{\tau}(\bmx) W_{\rho|\tau}(\x)^\alpha = 1,
\end{equation}
\nick{so...}.
The converse holds by inspection.

@@

4. \nick{This must hold due to~\cref{thm:H2D}}
\end{proof}
\nick{Combining ALL the properties above (and nothing more) leads to the general bound}

>>>>

\begin{theorem}\label{thm:DSchur}
	Let $\alpha = \frac{2a}{2b-1}$ for any positive integers $a,b$ with $a \geq b$. 
	Then, $D_\alpha$ is Schur-convex, i.e. let $\w, \w' \in \mathbb{R}^N$ be quasi-distributions and $\r, \r' \in \mathbb{R}^N$ be probability distributions with positive rational entries given by $r_i = a_i/K$ and $r_i' = a_i'/K$ for positive integers $a_i, a_i'$ and $K = \sum_{i=1}^N a_i = \sum_{i=1}^{N'} a_i'$.
	Then, we have $D_\alpha(\w || \r) \geq H_\alpha(\w' || \r')$, whenever $(\w, \r) \succ (\w', \r')$.
\end{theorem}
\begin{proof}
	The statement $(\w, \r) \succ (\w', \r')$ is equivalent to $\Gamma_{\bma}(\w) \succ \Gamma_{\bma'}(\w')$.
	Therefore, due to~\cref{thm:HSchur} we have
	\begin{equation}
		H_\alpha(\Gamma_{\bma}(\w)) \leq H_\alpha(\Gamma_{\bma'}(\w'))
	\end{equation}
	which due to~\cref{thm:H2D} is equivalent to
	\begin{equation}
		D_\alpha(\w ||\r) \geq D_\alpha(\w' ||\r').
	\end{equation}
\end{proof}

@@

1. $D_\alpha$ is Schur-convex and every pair $(\w, \r)$ majorizes $(\r', \r')$, so
\begin{equation}
	D_\alpha(\w || \r) \geq D_\alpha(\r' || \r') = \frac{1}{\alpha-1} \log_2 \sum_{i} r_i = 0.
\end{equation}

2. In the inequality of property 1, equality holds iff $L_{\w|\r}(x) = L_{\r'|\r'}(x) = L_{\r|\r}(x)$ for all $x$ due to~\cref{prop:rmajor} which holds iff $\w = \r$.

@@

4. This follows immediately from Schur-convexity of $D_\alpha$.
\end{proof}
\nick{Combining ALL the properties above (and nothing more) leads to the general bound}
